### 2020-03-30 Model Data Sheets and Code/Zaca MCF Mortality Model Results.Rmd
another final draft code (negligable change) plus ale graph images for chris

low_mean_acc <- low %>% 
  select (X1, Low) %>% 
  drop_na() %>% 
  filter (X1 == "Low") %>%
  mutate (Low = as.numeric(Low),
          class_acc = Low / 292) %>% 
 summarise(mean = (sum(class_acc)/iteration)) # used this code before to get mean: summarise(mean = mean(class_acc))
```

>>>>

low_mean_acc <- low %>% 
  select (X1, Low) %>% 
  drop_na() %>% 
  filter (X1 == "Low") %>%
  mutate (Low = as.numeric(Low),
          class_acc = Low / 292) %>% 
 summarise(mean = (sum(class_acc)/iteration)) # used this code before to get mean: summarise(mean = mean(class_acc))
